---
title: "KSU Agronomy R Workshop - Advanced 1 Agenda"
output: html_notebook
---

# 1) Setup  
```{r Setup, warning=F}
# Loading packages (everytime you open R)
library(tidyverse) # plotting and wrangling functions
library(readxl) # to read data from an excel file
library(lme4) # for mixed models
library(car) # Anova
library(broom.mixed) # model diagnostics
library(emmeans) # Anova means
library(multcomp) # pairwise comparisons
library(ggthemes) # ggplot customization

```


```{r Reading data}
soyk_w<- read_excel("../data/SoybeanWorkshopProcessed.xlsx", sheet=1)

# Checking first rows
soyk_w

```

# 2) Exploratory Plots 
```{r Point and curve}


```

# 3) Regression for one Location  
```{r Wrangling a bit more}
# Creating Krate as categorical (factor)
soyk_w<- soyk_w %>%
  mutate(fKrate_kgha=factor(Krate_kgha),
         fRep=factor(Rep),
         Location=factor(Location)) %>%
  filter(Location!="W1" | fRep!="1")

soyk_w

# Extracting only one location (S1)
soyk_w_S1

soyk_w_S1

```

- ANOVA vs. Regression 
- Fixed vs. Random effect

```{r RCBD model for Location A1}
options(contrasts = c("contr.sum", "contr.poly"))

```

```{r summary }

```

```{r Anova}

```

# 4) Model Assumptions  
Why is this important?  
Draw example on board showing a bad model for the data.  

```{r Extracting residuals information}


```


## 4.1) Within-group errors are iid ~ N(0, var2)  

On this plot, looking for:  
- Spread around zero  
- Homogeneity (no patterns)  
- Outliers (>3 or <-3)  

```{r Standardized Residuals vs. Fitted}


```

On this plot, looking for normality (points on top of line)
```{r Quantile-Quantile}

```


## 4.2) Random effects are iid ~ N(0,var1)  

On this plot, looking for normality.  
```{r QQ plot for fRep random effects}


```


# 5) Predicting with model results  
```{r Expected marginal means for K rates within Location}
soyk_reg_means_S1

soyk_reg_means_S1

```
These above didn't work so well.  
It give us the average K_pct at the average Krate.  
Not very useful I suppose.  

```{r Predicting}

```

# 6) Automating analysis for all Locations with group_by(), nest(), and map()  
```{r Automated Regression ANOVA diagnostics and prediction for all Locations }

soyk_reg_all 

```

```{r Checking ANOVAs}

```

```{r Checking Residuals}

```

# 7) Plotting it all  
```{r Plotting all with regression lines}



```


# Parting words
- Will share resources via email (cheatsheets, my blog)

- Will share a survey. Please respond to help in improving next workshops

- For those who reply to survey, I will share my entire project (reproducible)

- After a week, will share with everyone else only the scripts (included in the project)

- Thanks!




