---
title: "KSU Agronomy R Workshop - Advanced 1 Agenda"
output: html_notebook
---

# 1) Setup  
```{r Setup, warning=F}
# Loading packages (everytime you open R)
library(tidyverse) # plotting and wrangling functions
library(readxl) # to read data from an excel file
library(lme4) # for mixed models
library(car) # Anova
library(broom.mixed) # model diagnostics
library(emmeans) # Anova means
library(multcomp) # pairwise comparisons
library(ggthemes) # ggplot customization

```


```{r Reading data}
soyk_w<- read_excel("../data/SoybeanWorkshopProcessed.xlsx", sheet=1)

# Checking first rows
soyk_w

```

# 2) Exploratory Plots 
```{r Point and curve}
ggplot(soyk_w, aes(x=Krate_kgha, y=K_pct))+
  geom_point(aes(color=Location))+
  geom_smooth(method="lm")+
  facet_grid(.~Location)

```

# 3) Regression for one Location  
```{r Wrangling a bit more}
# Creating Krate as categorical (factor)
soyk_w<- soyk_w %>%
  mutate(fKrate_kgha=factor(Krate_kgha),
         fRep=factor(Rep),
         Location=factor(Location)) %>%
  filter(Location!="W1" | fRep!="1")

soyk_w

# Extracting only one location (S1)
soyk_w_S1<- soyk_w %>%
  filter(Location=="S1")

soyk_w_S1

```

- ANOVA vs. Regression 
- Fixed vs. Random effect

```{r RCBD model for Location A1}
options(contrasts = c("contr.sum", "contr.poly"))

soyk_reg_S1<- lmer(K_pct ~ (1|fRep) +
                     Krate_kgha,
                   data=soyk_w_S1)

```

```{r summary }
summary(soyk_reg_S1)
```

```{r Anova}
Anova(soyk_reg_S1, type=3)
```

# 4) Model Assumptions  
Why is this important?  
Draw example on board showing a bad model for the data.  

```{r Extracting residuals information}
soyk_reg_aug_S1<-augment(soyk_reg_S1)

soyk_reg_aug_S1$.stdresid<- resid(soyk_reg_S1, type="pearson", scaled=T)

```


## 4.1) Within-group errors are iid ~ N(0, var2)  

On this plot, looking for:  
- Spread around zero  
- Homogeneity (no patterns)  
- Outliers (>3 or <-3)  

```{r Standardized Residuals vs. Fitted}
ggplot(soyk_reg_aug_S1, aes(x=.fitted, y=.stdresid))+
  geom_point(aes(color=fRep))+
  geom_hline(yintercept = c(-3,0,3), color="orange")+
  geom_smooth()

```

On this plot, looking for normality (points on top of line)
```{r Quantile-Quantile}
ggplot(soyk_reg_aug_S1, aes(sample=.stdresid))+
  stat_qq()+
  stat_qq_line()
```


## 4.2) Random effects are iid ~ N(0,var1)  

On this plot, looking for normality.  
```{r QQ plot for fRep random effects}
randeff_Rep_A1<- ranef(soyk_reg_S1)[[1]]

ggplot(randeff_Rep_A1, aes(sample=`(Intercept)`))+
  stat_qq()+
  stat_qq_line()

```


# 5) Predicting with model results  
```{r Expected marginal means for K rates within Location}
soyk_reg_means_S1<- emmeans(soyk_reg_S1,
                            ~Krate_kgha)

soyk_reg_means_S1

```
These above didn't work so well.  
It give us the average K_pct at the average Krate.  
Not very useful I suppose.  

```{r Predicting}
soyk_reg_aug_S1 %>%
  ggplot(aes(y=.fixed, x=Krate_kgha))+
  geom_line()+
  geom_point(aes(y=K_pct))
```

# 6) Automating analysis for all Locations with group_by(), nest(), and map()  
```{r Automated Regression ANOVA diagnostics and prediction for all Locations }

soyk_reg_all <- soyk_w %>%
  group_by(Location) %>%
  nest() %>%
  # Fitting RCBD model
  mutate(mod=map(data,
                 ~lmer(K_pct ~ 
                         (1|fRep) + 
                         Krate_kgha,
                       data=.x))) %>%
  # Anova 
  mutate(Anova=map(mod,
                   ~Anova(.x, type=3))) %>%
  # Augmenting (for diagnostics and predictions)
  mutate(aug=map(mod,
                 ~augment(.x))) %>%
  # Adding standardized residuals 
  mutate(augstd=map2(aug,mod,
                    ~mutate(.data=.x, 
                            .stdresid=resid(.y,
                           type="pearson",
                           scaled=T)))) %>%
  # Checking residuals 
  mutate(diag1=map2(augstd,Location,
                   ~ggplot(data=.x, aes(x=.fitted, y=.stdresid))+
                     geom_point(aes(color=fRep))+
                     geom_hline(yintercept = c(-3,0,3), color="orange")+
                     labs(title=paste0(.y))
  ))

```

```{r Checking ANOVAs}
soyk_reg_all$Anova
```

```{r Checking Residuals}
soyk_reg_all$diag1
```

# 7) Plotting it all  
```{r Plotting all with regression lines}
soyk_reg_all %>%
  unnest(augstd) %>%
  ggplot(aes(x=Krate_kgha, y=K_pct, color=Location))+
  geom_point(aes(shape=Location), size=2, alpha=.6)+
  #facet_wrap(.~Location)+
  geom_line(aes(y=.fixed, linetype=Location), size=1)+
  labs(x="K Rate (kg K2O/ha)", y="Plant K (%)")+
  theme_solarized_2()+
  scale_color_tableau()+
  theme(legend.position = "bottom")+
  ggsave("../output/Regression.png", width = 5, height = 4)


```




